Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-11-06 Notebook LaTEX/EB is the key to IAGP/main.tex
>w<, a lot of changes

\section{Linear convergence for the proximal problem in the inner loop}
    In this section, we continue the discussion from Section \ref{sec:optz-inxt-pp-problem}. 
    As an important reminder, we will fix the vector $y \in \RR^n$, which is in the inexact proximal problem as a constant in this entire section. 
    \par
    The inner loop is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
    To accomplish let's assume that the outer loop iteration $k$ is fixed throughout this entire section.
    Now let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
    \begin{align*}
        x_k \approx_\epsilon \hprox_{\lambda g}(y_k - \lambda \nabla f(y_k)). 
    \end{align*}
    Unfortunately recall that $g = \omega \circ A$ in the context of the outer loop hence it's impossible to directly evaluate the proximal operator of $g$ and hence we optimize the function $\Phi_\lambda$ as given by \eqref{eqn:primal-pp}. 
    \par
    In this section, we will show that there exists an algorithm generating the sequences $z_n, v_n$ such that $\mathbf G_\lambda (z_n, v_n)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions. 
    Using results available in the literature, we will characterize the exact scenarios of $\omega \circ A$ when this is possible to achieve. 
    To start, the following assumption is the general error bound condition of a convex with additive composite structure.

@@

            \item the objective function is given by $F = f + g$. 
        Let the gradient mapping $\mathcal G_{\tau}$ be defined as: $\mathcal G_\tau(x) := \tau (x - T_\tau(x))$     
        In addition, assume that the optimization problem $F$ satisfies the error bound condition if it has for all $\tau \ge L, x \in \RR^n$ there exists $\gamma > 0$: 

@@

        \begin{definition}[quasi-strongly convex function]

        \end{definition}
        \begin{definition}[quadratic growth]

        \end{definition}
        \begin{fact}[error bound quadratic growth equivalence]

        \end{fact}
        \begin{fact}[Hoffman error bound]

        \end{fact}
        \begin{fact}[A characterization of quasi strongly convex function]

>>>>

\section{Linear convergence for the proximal problem in the inner loop}
    In this section, we continue the discussion from Section \ref{sec:optz-inxt-pp-problem}. 
    As an important reminder, we will fix the vector $y \in \RR^n$, which is in the inexact proximal problem as a constant in this entire section. 
    The inner loop is another algorithm that evaluates $x_k \approx_\epsilon T_{(B_k + \rho_k)}(y_k)$ for a given value of $\epsilon, B + \rho$ and at the point $y_k$. 
    To accomplish let's assume that the outer loop iteration $k$ is fixed throughout this entire section.
    Now let $\lambda = (B_k + \rho_k)^{-1}$, the algorithm needs to resolve the following equivalent inexact proximal point problem: 
        x_k \approx_\epsilon \hprox_{\lambda g}(y_k - \lambda \nabla f(y_k)). 
    Unfortunately recall that $g = \omega \circ A$ in the context of the outer loop hence it's impossible to directly evaluate the proximal operator of $g$ and hence we optimize the function $\Phi_\lambda$ as given by \eqref{eqn:primal-pp}. 
    In this section, we will show that there exists an algorithm generating the sequences $z_n, v_n$ such that $\mathbf G_\lambda (z_n, v_n)$ converges linearly if $\Psi_\lambda$ satisfies the error bound conditions. 
    Using results available in the literature, we will characterize the exact scenarios of $\omega \circ A$ when this is possible to achieve. 
    To start, the following assumption is the general error bound condition of a convex with additive composite structure. 
    \begin{definition}[the exact proximal gradient and gradient mapping]\;\label{def:pg-and-gm}\\
        Let $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a differentiable function and, $g: \RR^n \rightarrow \overline \RR$ is closed convex and proper. 
        We define the exact proximal gradient mapping and, gradient mapping: 
            \item The proximal gradient operator $T_{\tau}(x) := \hprox_{\tau^{-1}g}(x - \tau^{-1}\nabla f(x))$,
            \item and the gradient mapping operator $\mathcal G_\tau(x) := \tau (x - T_\tau(x))$. 
    \begin{definition}[error bound]\;\label{def:err-bnd}\\
        Let $F = f + g$ where $f:\RR^n \rightarrow \RR$ is a differentiable function and, $g: \RR^n \rightarrow \overline \RR$ is closed convex and proper. 
        Assume the set of minimizers $S = \argmin_{x} F \neq \emptyset$. 
        Let $\gamma> 0$, and let proximal gradient mapping $T_\tau$, gradient mapping $\mathcal G_\tau$ of $F = f + g$ as given by Definition \ref{def:pg-and-gm}. 
        Then their sum $F = f + g$ satisfies the error bound condition if there exists $\gamma > 0$ such that 

@@

            \item the objective function is given by $F = f + g$ and, it satisfis error bound (Definition \ref{def:err-bnd}). 

@@

        The goal of this section is to show that specific type of nonsmooth function $\omega$ that common appear in applications satisfies the error bound condition for the proximal problem, and hence the results from the previous section are applicable. 
        \begin{definition}[quasi-strongly convex function {\cite[Definition 1]{necoara_linear_2019}}]
            Let $f:\RR^n \rightarrow \RR$ be differentiable. 
            Let $X \subseteq \RR^n$ and suppose that the set of minimizers $X^+=\argmin_{x \in X} f(x) \neq \emptyset$ exists and, denote $f^+$ to be the minimum of $f$ on $X$. 
            It is quasi strongly-convex on the set $X \subseteq \RR^n$ if $\exists \kappa > 0$ such that $\forall x \in X$, let $\bar x = \Pi_{X^+} x$, it satisfies
                f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle + \frac{\kappa}{2}\Vert x - \bar x\Vert^2 \quad \left(\forall x \in X\right). 
        \begin{definition}[quadratic growth]\label{def:q-growth}
            Let $F = f + g$ where $f: \RR^n \rightarrow \RR$ be differentiable and, $g: \RR^n \rightarrow \overline \RR$ be closed convex and, proper. 
            Assume in addition that the set of minimizer $S := \argmin_{x\in \RR^n} F \neq \emptyset$, denote $F^+$ to be the minimum, then it satisfies the quadratic growth conditions if there exists $\kappa > 0$ such that
                (\forall x \in \RR^n)\; F(x) \ge F^+ + \frac{\kappa}{2}\dist^2(x | S).
        The following theorem shows that under the standard framework of smooth nonsmooth additive compsitive objective function, the quadratic growth condition implies error bound.
        \begin{theorem}[quadratic growth implies error bound]\;\label{thm:qfg-means-eb}\\
            Let $f: \RR^n \rightarrow $
            Denote $x^+ = T_\tau(x)$, $\bar x = \Pi_{S}x$, and $\bar x ^+ = \Pi_{S} x^+$. 
            We use the exact proximal gradient inequality by applying Theorem \ref{thm:inxt-pg-ineq} with $\epsilon = 0, \rho = 0$ and, $z = \bar x^+$ gives: 
                0 &\ge F(x^+) - F(\bar x^+) - \tau \langle \bar x^+ - x^+, x^+ - x\rangle - \frac{\tau}{2}\Vert x - x^+\Vert^2
                &\underset{(1)}{\ge} \frac{\kappa}{2}\Vert x^+ - \bar x^+\Vert^2
                - \Vert \tau(\bar x^+ - x^+)\Vert \Vert x^+ - x\Vert - \frac{1}{2\tau }\Vert \tau(x - x^+)\Vert^2
                &= \frac{\kappa}{2}\left\Vert
                    x^+ - \bar x^+
                - \frac{\tau}{2}\left(
                    2\left\Vert
                        \bar x^+ - x^+
                    \right\Vert \left\Vert
                        x^+ - x
                    \right\Vert
                    + \Vert x - x^+\Vert^2
                \frac{\kappa + \tau}{2}\left\Vert x^+ - \bar x^+ \right\Vert^2 
                - \frac{\tau}{2}(
                    \Vert \bar x^+ - x^+\Vert + \Vert x^+ - x\Vert
                )^2
                &\underset{(3)}{\ge}
                \frac{\kappa + \tau}{2}\left(
                    \Vert x - \bar x\Vert - \Vert x - x^+\Vert
                - \frac{\tau}{2}(\Vert x - \bar x\Vert)^2
                0 &\ge
                \sqrt{\kappa + \tau}\left(
                    \Vert x - \bar x\Vert - \Vert x - x^+\Vert
                - \sqrt{\tau}(\Vert x - \bar x\Vert)
                &= (\sqrt{\kappa + \tau} - \sqrt{\tau})\Vert x - \bar x \Vert
                - \sqrt{\kappa + \tau} \Vert x - x^+\Vert. 
            At (1), we used quadratic growth assumption and substitute the inequality of Definition \ref{def:q-growth}, and the Cauchy inequality. 
            At (2), consider substituting $a = \bar x^+ - x^+, b = x^+ - x$, so the second terms with the parenthesis has inside $2\Vert a\Vert\Vert b\Vert + \Vert b\Vert^2 = (\Vert a\Vert + \Vert b\Vert)^2 - \Vert a\Vert^2$. 
            At (3), we used the properties of projecting onto the set set of minimizer $S$, which gives:
                & \Vert x - \bar x\Vert \le 
                \Vert x - \bar x^+\Vert 
                \le \Vert x - x^+\Vert + \Vert x^+ - \bar x^+\Vert
                & \Vert x - \bar x\Vert - \Vert x - x^+\Vert
                \le \Vert x^+ - \bar x^+\Vert
            Finally, re-arranging the results it should yield the following inequality: 
                \Vert \mathcal G_\tau(x)\Vert 
                &= \Vert \tau(x - x^+)\Vert 
                &\ge \tau\left(
                    \frac{\sqrt{\kappa + \tau} - \sqrt{\tau}}{\sqrt{\kappa + \tau}}
                \right)\Vert x - \bar x\Vert
                &= \frac{\tau\kappa}{\kappa + \tau + \sqrt{\tau(\kappa + \tau)}}
                \Vert x - \bar x\Vert. 
            The above is error bound conditions as defined in Definition \ref{def:err-bnd}, with $\gamma = \frac{\tau\kappa}{\kappa + \tau + \sqrt{\tau(\kappa + \tau)}}$. 
            This theorem is not exactly a new result. 
            We adapted claim and the proof here so the notations stays consistent and to make it self contained.

        \end{remark}
        \begin{fact}[Hoffman error bound]

        \end{fact}
        \begin{fact}[a type of quasi strongly convex function]

### 2025-11-06 Notebook LaTEX/R-WAPG/2025-06-10-00-paper.tex
>w<, changes
>w<, a lot of changes

            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat\gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

                F(x_k) - F^* + R_k + \frac{\rho_{k - 1}L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2

@@

                F(x_k) - F^* + R_k + \max(1, \rho_{k - 1})\frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2

@@

                F(x_k) - F^* + R_k + \frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2

@@

                F(x_1) - F^* + R_1 + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2

@@

@@

        Finally, since $\mu = 0$, Proposition \ref{prop:r-wapg-momentum-repr} applies with the momentum term simplifies into $\alpha_{k + 1}(\alpha_k^{-1} - 1)$. 

@@

        This section showcases results for the numerical experiments conducted using FR-WAPG algorithm (Algorithm \ref{alg:free-rwapg}), and compare with other APG algorithms in the literatures: the V-FISTA, and M-FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.

@@

        The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, V-FISTA and M-FISTA.
        We measure the aggregate statistics of the base two logarithms of the normalized optimality gap (NOG), at each iteration $k$ with the same initialization conditions given for all algorithms.
        Given $x_k$, and minimum $F^*$, we define the normalized optimality gap:
        \newcommand{\NOG}{\text{\textbf{NOG}}}

@@

                \NOG_k
            \text{ with }
            \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}.
        Since it's not the case that $F^*$ is always known in prior, we will use the minimum of all $F(x_k)$ across all algorithms, all iterations $k$ as the surrogate for $F^*$ when the true value is unavailable.
        We consider the norm of the gradient mapping $\Vert \mathcal G_L(y_k)\Vert < \epsilon$ as a termination conditions for all test algorithms.
        The $L$ can change during each iteration if it's obtained through the specified Lipschitz line search routine.
        \subsubsection{Simple convex quadratic}
            Consider $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ where
                f(x) = (1/2)\langle x, A x\rangle.
            $A$ is set to be a positive semi-definite diagonal matrix, so the problem admits the minimizer $x^* = \mathbf 0$ (which is not unique) with minimum being zero.
            We apply Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA.

>>>>

            F(x_{k + 1}) - F(x^*) + R_{k + 1} + \frac{\hat\gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2
            F(x_{k + 1}) - F(x^*) + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

                F(x_k) - F(x^*) + R_k + \frac{\rho_{k - 1}L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2

@@

                F(x_k) - F(x^*) + R_k + \max(1, \rho_{k - 1})\frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2

@@

                F(x_k) - F(x^*) + R_k + \frac{L \alpha_{k - 1}^2}{2}\Vert v_k - x^*\Vert^2

@@

@@

            \item Since $\mu = 0$, by Proposition \ref{prop:wapg-first-equivalent-repr}, the extrapolated iterate has $y_k = x_{k + 1} + \alpha_{k + 1}(\alpha_k^{-1} - 1)$

@@

        It remains to verify whether the sequence $\alpha_k$ is still valid, by which it means that $\alpha_k \in (0, 1)$ for all $k \ge 1$. 
        We will soon reveal that it will be true in the part that comes. 

@@

        In this section, we will show the numerical experiments results of algorithm (Algorithm \ref{alg:free-rwapg}) in this section then, we compare with other APG algorithms in the literatures: the V-FISTA, and FISTA algorithm described in Section (10.7.7, 10.7.6) by Beck \cite{beck_first-order_2017}.

@@

        % The equivalences highlighted in Proposition \ref{prop:r-wapg-momentum-repr} allows us to compare the sequence of iterates $(x_k)_{k \ge 1}, (y_k)_{k \ge0}$ for R-WAPG, V-FISTA and M-FISTA.
        We will now introduce the global setup of our numerical experiments. 
        To compare the convergence of different algorithms, we measure the logarithm of the relative optimaity gap $\delta_k$ which we defined: 
        % \newcommand{\NOG}{\text{\textbf{NOG}}}

@@

                \frac{F(x_k) - F^*}{F(x_0) - F^*}
        We give the same inigial guess $x_0$ for all algorithms.
        Since $F^*$ is not always known in prior, we used the minimum of all $F(x_k)(1 - 2^{53})$ across all algorithms to estimate the minimum $F^*$ when it's not avaiable. 
        Fix some $\epsilon > 0$. 
        The termination condition is $\Vert \mathcal G_L(y_k)\Vert < \epsilon$ for all algorithms.
        We implemented line search for Lipschitz smoothness constant $L$ only for FISTA. 
        For FR-WAPG and V-FISTA, an over estimate of the Lipschitz modules is given. 
        \subsubsection{Experiments with a simple convex quadratic function}
            Consider $\min_{x \in \RR^n} \{F(x):= f(x) + 0\}$ given by $f(x) = (1/2)\langle x, A x\rangle$. 
            Here, $A$ is set to be a positive semi-definite diagonal matrix, hence problem is a convex quadratic and one of its minimizer is $x^* = \mathbf 0$,  with minimum being zero.
            We repeat the same experiment for Algorithm \ref{alg:free-rwapg}, M-FISTA, and V-FISTA for 30 times with different initial guesses. 

### 2025-11-06 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, a lot of changes

% BIB STYLES SETTINGS ----------------------------------------------------------
\setbeamertemplate{bibliography item}{\insertbiblabel}
\setbeamerfont{bibliography item}{size=\footnotesize}
\setbeamerfont{bibliography entry author}{size=\footnotesize}
\setbeamerfont{bibliography entry title}{size=\footnotesize}
\setbeamerfont{bibliography entry location}{size=\footnotesize}
\setbeamerfont{bibliography entry note}{size=\footnotesize}
% \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
\bibliographystyle{siam}

@@

\section{Introduction and background}
    \subsection{Motivations}
        \begin{frame}{Nesterov's accelerated gradient in 1983}
            \begin{block}{Nesterov's accelerated gradient in 1983}
                Initialized $x_0 = y_0 \in \RR^n$. 
                The original formulation by Nesterov in 1983 \cite{nesterov_method_1983} has
                {\small
                \begin{align*}
                    & x_{k + 1} := y_k - L^{-1}\nabla F(y_k),
                    \\
                    & t_{k + 1} := 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
                    \\
                    & \theta_{k + 1} := (t_{k} - 1)/t_{k + 1}, \label{eqn:example-algorithm}
                    \\
                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
                \end{align*}    
                }
            \end{block}
            When $F$ is convex and, $L$ Lipschitz smooth. 
            If minimizer $x^+$ exists, then: 
            \begin{itemize}
                \item a convergence rate of $\mathcal O(1/k^2)$ for $(F(x_k) - F(x^+))_{k \ge 1}$;
                \item this convergence rate is optimal in the sense as proposed by Nesterov \cite{nesterov_lectures_2018}.
            \end{itemize}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part I}
            Major results from the literature regarding different choices for the momentum sequence $(t_k)_{k \ge 0}$. 
            \begin{block}{Beck, Teboulle 2009 {\cite[Theorem 4.4]{beck_fast_2009-1}}}
                Commonly known by the name FISTA, it allows $(t_k)_{k}$: 
                \begin{align*}
                    (\forall k \ge 1)\quad t_k (t_k - 1) &\le t_{k - 1}^2. 
                \end{align*}    
                When $t_k (t_k - 1) = t_{k - 1}^2$, it yields $\mathcal O(1/k^2)$ convergence rate of optimality gap
            \end{block}
            \begin{block}{Chambolle, Dossal 2015 \cite[Theorem 4.1]{chambolle_convergence_2015}}
                If $t_k = (k + a -1)/a$ in which case this gives $\theta_{k} = \frac{k - 2}{k + a - 1}$, then $(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.    
            \end{block}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part II}
            A finetuned constant momentum sequence gives optimal linear convergence rate for specific strongly convex objective. 
            \begin{block}{
                Nesterov 2018 {\cite[Theorem 2.2.3]{nesterov_lectures_2018}}, 
                Beck 2017 {\cite[Theorem 10.42]{beck_first-order_2017}}
            }
                If in addition whe $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, and $\mu > 0$ strongly convex, then for $(\theta_k)_{k\ge 0}$ such that: 
                \begin{align*}
                    \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}, 
                \end{align*}
                it gives $\mathcal O\left(\left(1 - \sqrt{\mu/L}\right)^k\right)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 
            \end{block}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part III}
            The cases when the inequality of Nesterov's rule is not satisfied had been investigated as well.
            \begin{block}{Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2018}}
                If $\theta_k = \frac{k}{k + b}\;\forall k \ge 0$ where $b \in (0, 3)$ then, the optimality gap has a convergence rate of $\mathcal O(1/k^{2b/3})$. 
            \end{block}
        \end{frame}

@@

                How much can we relax the choice of the sequence $\theta_k$ and retain an upper bound for the convergence rate? 

@@

                We made an algorithm which we called ``Free R-WAPG", it estimates the strong convexity constant $\mu$ using the Bregman Divergence at two successive iterates when the algorithm is running. 
                This information is used to determine the sequence $(\alpha_k)_{k \ge 0}$, and used to visualized our theoretical upper bound. 

@@

@@

            Starting in this section, we will highlight key theoretical results that will allow the unifying convergence rate for Euclidean variants of FISTA in the literature.

@@

@@

                \item $L = 1, \mu = 10^{-5}$ are known in prior. 

@@

            A realization of $x_0 \sim \mathcal N(I, \mathbf 0)$ is used for V-FISTA, M-FISTA (Monotone restarted FISTA) and Free R-WAPG. 

@@

                    Statistics for experiments with simple convex quadratic for V-FISTA, M-FISTA, and R-WAPG.

@@

                \item Let $F_{\min}$ be the smallest value of $F(x_k)$, for all algorithms, over all trials, we estimate $F^+$ by $F^+ = F_{\min}*(1 - 2^{53})$. 

@@

        \begin{frame}{LASSO Results plotted}
            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 20 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA. 

@@

\section{References and draft on arxiv}
    \begin{frame}{Acknowledgement}
        The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
        \par
        The travel of HL to this conference is supported by the NSF grant DMS-2526465.
    \end{frame}
    \begin{frame}{Thanks for the participations. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}{References}        
        \bibliography{references/R-WAPG.bib}
    \end{frame}

>>>>

% BIB STYLES SETTINGS ----------------------------------------------------------
\setbeamertemplate{bibliography item}{\insertbiblabel}
\setbeamerfont{bibliography item}{size=\tiny}
\setbeamerfont{bibliography entry author}{size=\tiny}
\setbeamerfont{bibliography entry title}{size=\tiny}
\setbeamerfont{bibliography entry location}{size=\tiny}
\setbeamerfont{bibliography entry note}{size=\tiny}
% \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
\bibliographystyle{siam}

@@

\section{Introduction and background}
    \subsection{Motivations}
        \begin{frame}{Nesterov's accelerated gradient in 1983}
            \begin{block}{Nesterov's accelerated gradient in 1983}
                Initialized $x_0 = y_0 \in \RR^n$. 
                The original formulation by Nesterov in 1983 \cite{nesterov_method_1983} has
                {\small
                \begin{align*}
                    & x_{k + 1} := y_k - L^{-1}\nabla F(y_k),
                    \\
                    & t_{k + 1} := 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right),
                    \\
                    & \theta_{k + 1} := (t_{k} - 1)/t_{k + 1}, \label{eqn:example-algorithm}
                    \\
                    & y_{k + 1} := x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k).
                \end{align*}    
                }
            \end{block}
            When $F$ is convex and, $L$ Lipschitz smooth. 
            If minimizer $x^+$ exists, then: 
            \begin{itemize}
                \item a convergence rate of $\mathcal O(1/k^2)$ for $(F(x_k) - F(x^+))_{k \ge 1}$;
                \item this convergence rate is optimal in the sense as proposed by Nesterov \cite{nesterov_lectures_2018}.
            \end{itemize}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part I}
            Major results from the literature regarding different choices for the momentum sequence $(t_k)_{k \ge 0}$. 
            \begin{block}{Beck, Teboulle 2009 {\cite[Theorem 4.4]{beck_fast_2009-1}}}
                Commonly known by the name FISTA, it allows $(t_k)_{k \ge 0}$: 
                \begin{align*}
                    (\forall k \ge 1)\quad t_k (t_k - 1) &\le t_{k - 1}^2. 
                \end{align*}    
                When $t_k (t_k - 1) = t_{k - 1}^2$, it yields $\mathcal O(1/k^2)$ convergence rate of optimality gap
            \end{block}
            \begin{block}{Chambolle, Dossal 2015 \cite[Theorem 4.1]{chambolle_convergence_2015}}
                If $t_k = (k + a -1)/a$ in which case this gives $\theta_{k} = \frac{k - 2}{k + a - 1}$, then $(x_k)_{k \ge 0}$ has weak convergence in Hilbert space for all $a > 2$.    
            \end{block}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part II}
            A finetuned constant momentum sequence gives optimal linear convergence rate for specific strongly convex objective. 
            \begin{block}{
                Nesterov 2018 {\cite[Theorem 2.2.3]{nesterov_lectures_2018}}, 
                Beck 2017 {\cite[Theorem 10.42]{beck_first-order_2017}}
            }
                If in addition whe $F:\RR^n \rightarrow \RR$ is $L$ smooth gradient, and $\mu > 0$ strongly convex, then for $(\theta_k)_{k\ge 0}$ such that: 
                \begin{align*}
                    \theta_k = \frac{\sqrt{L/\mu} - 1}{\sqrt{L/\mu} + 1}, 
                \end{align*}
                it gives $\mathcal O\left(\left(1 - \sqrt{\mu/L}\right)^k\right)$ convergence rate for $(F(x_k) - F(x^+))_{k \ge 1}$. 
            \end{block}
        \end{frame}
        \begin{frame}{Other choices for the momentum sequence part III}
            The cases when the inequality of Nesterov's rule is not satisfied had been investigated as well.
            \begin{block}{Apidopoulos et al. 2018 \cite{apidopoulos_convergence_2020}}
                If $\theta_k = \frac{k}{k + b}\;\forall k \ge 0$ where $b \in (0, 3)$ then, the optimality gap has a convergence rate of $\mathcal O(1/k^{2b/3})$. 
            \end{block}
        \end{frame}

@@

                How much can we relax the choice of the sequence $(t_k)_{k \ge 0}, (\theta_k)_{k \ge 0}$ and retain an upper bound for the convergence rate? 

@@

                We made an algorithm which we called ``Free R-WAPG", it estimates the strong convexity constant $\mu$ using the "Bregman Divergence" at two successive iterates when the algorithm is running. 
                This information is then used to determine the sequence $(\alpha_k)_{k \ge 0}$ while the algorithm is running. 

@@

            This will come at the last section. 
            The quoted "Bregman Divergence" will be explained in a future slide. 

@@

            Starting in this section, we will highlight key theoretical results that unify the convergence rate for Euclidean variants of FISTA in the literature.

@@

        \begin{frame}{The Bregman Divergence}
            We will now explain the "Bregman Divergence" that will be used in our numerical experiment in a later section. 
            \begin{definition}[Bregman Divergence]
                Let $f: \RR^n \rightarrow \RR$ be a differentiable function. 
                We define the Bregman divergence to be: 
                    D_f(x, y): \RR^n \times \RR^n \rightarrow \RR
                    \defeq (x, y)\mapsto f(x) - f(y) - \langle \nabla f(y), x - y\rangle.
            \begin{remark}
                Here, $f$ is not necessarily Legendre \cite[Definition 1]{bauschke_descent_2017}, as in the Legendre Transformation of convex analysis. 
            \end{remark}

@@

                \item $L = 1, \mu = 10^{-5}$ are known in prior. Feed $L, \mu$ to V-FISTA and, $L$ to Free R-WAPG. 

@@

            A realization of $x_0 \sim \mathcal N(I, \mathbf 0)$ is used for V-FISTA, FISTA and Free R-WAPG. 

@@

                    Statistics for experiments with simple convex quadratic for V-FISTA, FISTA, and R-WAPG.

@@

                \item Let $F_{\min}$ be the smallest value of $F(x_k)$, for all algorithms, over all trials, we estimate $F^+$ by $F^+ = (1 - 2^{53})F_{\min}$. 

@@

        \begin{frame}{Convergence}
            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(\mathbf 0, I)$ realized, 20 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for FISTA, Free R-WAPG, and V-FISTA. 

@@

\section{References and draft on arxiv}
    \begin{frame}{Acknowledgement}
        The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.
        \par
        The travel of HL to this conference is supported by the NSF grant DMS-2526465.
    \end{frame}
    \begin{frame}{Thanks for the participations. Merci pour les participations.}
        Our paper can be found on arxiv using the following QR code: 
        \begin{figure}
            \centering
            \includegraphics[width=15em]{assets/paper-qrcode.png}
        \end{figure}
        Questions?
    \end{frame}
    \begin{frame}[allowframebreaks]{References}        
        \tiny
        \bibliography{references/R-WAPG.bib}
